\documentclass {book}
\pagenumbering{roman}
\begin {document}
	\title{JavaScript Basics For Absolute Beginners}
	\author{Mohammed Abdulhady}
	\date{\today}
	\maketitle	
	\tableofcontents
	\chapter{Introduction}
	\section{History of JavaScript}
	JavaScript was created in 1995 by Brendan Eich who worked at Netscape. JavaScript was originally named Mocha by Marc Andreessen, the founder of Netscape. The name was changed to LiveScript and then to JavaScript. It was some kind of a marketing move because of the popularity of Java at that time.
	\section{What is JavaScript?}
	JavaScript is an object-oriented programming language that is used to make web pages interactive and creating web applications. JavaScript is an interpreted language, it needs an interpreter to translate the codes and executes the program. The interpreter, which is the browser in our case, executes instructions directly line by line without previously compiling it into machine language.\\\\
	Many people confused between Java (developed in the 1990s at Sun Microsystems) and JavaScript. They are completely different. Only the names are similar.
	\section{Why JavaScript}
	JavaScript is a very simple, powerful and popular programming language. It has become an essential technology along with HTML and CSS.\\
	You will need to learn JavaScript if you want to get into web development, if you are planning to be a front-end or you can even use it for back-end development.\\
	As o this moment, JavaScript has extended to desktop apps development, mobile apps development and games development.
	It has become a very important and useful skill to master.
\end {document}


